Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2019-04-06 Manuscript/manuscript.Rmd
Add references about distance

While direct overlaps represent the most straightforward measure of functional associations, they do not account for indirect relationships shown to be one of the major driving force of genome regulation [??? REFS]. The most prominent example maybe the enhancer-promoter relationships, with enhancers are frequently located hundreths or thousands bases away from their target promoters [??? REFS]. The use of distances between TAD boundaries and genomic annotations has largely been ignored. However, these distance features have the potential to offer a more accurate spatial representation of which genomic features are associated with TAD boundaries.

>>>>

While direct overlaps represent the most straightforward measure of functional associations, they do not account for distant relationships shown to be one of the major driving force of genome regulation [12426570, 24243018]. The most prominent example maybe the enhancer-promoter relationships, with enhancers are frequently located hundreths or thousands bases away from their target promoters [17086198, 24213634], or even on different chromosomes [15880101]. The use of distances between TAD boundaries and genomic annotations has largely been ignored. However, these distance features have the potential to offer a more accurate spatial representation of which genomic features are associated with TAD boundaries.
